Output Summary

### 2021-09-03 03-post-process/output-plots.Rmd
Add new parameters to output-plots
For the quantities representing upstream survival, added content for:

* MCMC diagnostics
* Posterior predictive checks
* Fit check plots
* Parameter summary plots

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  omega_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)
```

@@

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp
)

@@

@@

>>>>

# Migration survival: BON to LGR
L1 = "Migration Survival (BON to LGR)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_Rb_Ra[origin]", "sig_Lphi_Rb_Ra[origin]", "phi_Rb_Ra[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor)
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
phi_Rb_Ra_diags = rbind(tmp1, tmp2)

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  omega_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

# remove any summaries for nodes that don't have diagnostics
# e.g., if that "parameter" takes on a fixed value in the model
diags_table = diags_table[diags_table$n_params > 0,]
```

@@

# movement survival from BON to LGR
new = post_subset(post, "LGR_adults_new_dev", TRUE)
obs = post_subset(post, "LGR_adults_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
LGR_adults_bp = data.frame(
  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(LGR_adults_bp) = NULL

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp, LGR_adults_bp
)

@@

### BON Adults $\rightarrow$ LGR (NOR)

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

### BON Adults $\rightarrow$ LGR (HOR)

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[.+,origin]$", origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"))
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

## Movement Survival BON to LGR

```{r bon-to-lgr-bxp}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
```
